

# Understand Factors Affecting Wine Quality 
#### by Pallavi Mondhe

## Introduction
The wine quality- what factors determines the wine is good, bad or avarage? Can we tell the wine quality without having to taste it. I think it is quite possible, with data providing variables like 

   1 - fixed acidity (tartaric acid - g / dm^3)
   
   2 - volatile acidity (acetic acid - g / dm^3)
   
   3 - citric acid (g / dm^3)
   
   4 - residual sugar (g / dm^3)
   
   5 - chlorides (sodium chloride - g / dm^3
   
   6 - free sulfur dioxide (mg / dm^3)
   
   7 - total sulfur dioxide (mg / dm^3)
   
   8 - density (g / cm^3)
   
   9 - pH
   
   10 - sulphates (potassium sulphate - g / dm3)
   
   11 - alcohol (% by volume)

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
library(ggplot2)
library(gridExtra)
library(grid)
library(plyr)
library(GGally)
library(dplyr)


```

## Dataset
This dataset is public available for research. We have two datasets, about red and white wine. I will read the data for red wine as red_wine and for white wine as white_wine. And understand the data structure 

```{r echo=FALSE}

red_wine = read.csv(file.choose())
red_wine$X <- NULL

white_wine = read.csv(file.choose())
white_wine$X <- NULL

```
```{r}
str(red_wine)
summary(red_wine)

str(white_wine)
summary(white_wine)

```

We have the output as "quality". Now, I want to create new variable with factors good, bad and avarage. The 'quality' ranges between 0 (very bad) and 10 (very excellent)

```{r}
#for red wine
red_wine$rating <- ifelse(red_wine$quality < 5, 'bad', 
                      ifelse( red_wine$quality < 7, 'average', 'good'))

red_wine$rating <- ordered(red_wine$rating,
                       levels = c('bad', 'average', 'good'))
#for white wine
white_wine$rating <- ifelse(white_wine$quality < 5, 'bad', 
                      ifelse( white_wine$quality < 7, 'average', 'good'))

white_wine$rating <- ordered(white_wine$rating,
                       levels = c('bad', 'average', 'good'))


```

## Exploratory Data Analysis
## Univariate Plots
Lets plot the distribution of each variables. This way we can understand if the variable is Normally distributed, Positively Skewed or Negatively Skewes

```{r echo=FALSE, message=FALSE, warning=FALSE}
#first let's see distribution of quality

p <- ggplot(data = red_wine)

p2 <- ggplot(data = white_wine)

#red_wine quality distribution
qua_r <- p+ geom_histogram(aes(x= quality), fill = "white",color = "blue",binwidth = 1)+
  xlab("Red Wine Quality")+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))

#Red win rating

rating_r <- p+ geom_bar(aes(x= rating), fill = "white",color = "blue")+
  xlab("Red Wine Rating")+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))
  
#white_wine quality distribution
qua_w <- p2+ geom_histogram(aes(x= quality), fill = "white",color = "blue",binwidth = 1)+
  xlab("White Wine Quality")+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))

#white win rating

rating_w <- p2+ geom_bar(aes(x= rating), fill = "white",color = "blue")+
  xlab("White Wine Rating")+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))

grid.arrange(qua_r,rating_r,qua_w, rating_w, nrow= 2)

```

The the above plots, we can see most of the wines come under an avarage quality. I will have better understanding on this while creating the bivariate and multivariate plots. Let's see other variables distribution.

#### for red wine 
Let's see the distribution of acides and pH

```{r echo=FALSE, message=FALSE, warning=FALSE}
a1 <- p+ geom_histogram(aes(x= fixed.acidity), fill = "red",color= "black",binwidth = 1, alpha=0.3)+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))


a2 <- p+ geom_histogram(aes(x= volatile.acidity), fill = "red",color= "black",binwidth = 0.05, alpha=0.3)+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))+
  xlim(0,1)

a3 <- p+ geom_histogram(aes(x= citric.acid), fill = "red",color= "black",binwidth = 0.05, alpha=0.3)+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))+
  xlim(0,1)

a4 <- p+ geom_histogram(aes(x= pH), fill = "red",color= "black",binwidth = 0.1, alpha=0.3)+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))


grid.arrange(a1,a2,a3,a4,nrow=2)


```

The above graph shows the normal distribution for fixied.acidity, volitile.acidity and PH. We can say that these 3 variables are co-related. We will explore more about citric.acide in coming plots.

Distribution of SO2 and Sulphates

```{r echo=FALSE, message=FALSE, warning=FALSE}

s1 <- p+ geom_histogram(aes(x= free.sulfur.dioxide), fill = "red",color= "black",binwidth = 5, alpha=0.3)+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))


s2 <- p+ geom_histogram(aes(x= total.sulfur.dioxide), fill = "red",color= "black",binwidth = 10, alpha=0.3)+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))

s3 <- p+ geom_histogram(aes(x= sulphates), fill = "red",color= "black",binwidth = 0.02, alpha=0.3)+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))

grid.arrange(s1,s2,s3,nrow=2)

```

Though the free SO2 and total SO2 seem not normally distributed, they are co-related. both are positively skewed.


```{r echo=FALSE, message=FALSE, warning=FALSE}


p+ geom_histogram(aes(x= residual.sugar), fill = "red",color= "black",binwidth = 0.5, alpha=0.3)+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))

```

There few outliers present in residual.sugar. If we ignor those, the residual sugare is normally distributed

```{r echo=FALSE, message=FALSE, warning=FALSE}

p+ geom_histogram(aes(x= density), fill = "red",color= "black",binwidth = 0.001, alpha=0.3)+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))


```

Density distribution seems normal.

```{r echo=FALSE, message=FALSE, warning=FALSE}

p+ geom_histogram(aes(x= alcohol), fill = "red",color= "black",binwidth = 0.5, alpha=0.3)+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))

```

Distribution of Alcohol is positively skewed. we will explore more about alcohol and density in coming plots.

```{r echo=FALSE, message=FALSE, warning=FALSE}

p+ geom_histogram(aes(x= chlorides), fill = "red",color= "black",binwidth = 0.01, alpha=0.3)+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))

```

The clorides are normally distributed with few outliers.

#### for white wine
Let's see the distribution of acides and pH

```{r echo=FALSE, message=FALSE, warning=FALSE}

aw1 <- p2+ geom_histogram(aes(x= fixed.acidity), fill = "blue",color= "black",binwidth = 1, alpha=0.3)+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))


aw2 <- p2+ geom_histogram(aes(x= volatile.acidity), fill = "blue",color= "black",binwidth = 0.05, alpha=0.3)+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))+
  xlim(0,1)

aw3 <- p2+ geom_histogram(aes(x= citric.acid), fill = "blue",color= "black",binwidth = 0.05, alpha=0.3)+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))+
  xlim(0,1)

aw4 <- p2+ geom_histogram(aes(x= pH), fill = "blue",color= "black",binwidth = 0.1, alpha=0.3)+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))


grid.arrange(aw1,aw2,aw3,aw4,nrow=2)


```

The above graph shows the normal distribution for fixied.acidity, volitile.acidity and PH. We can say that these 3 variables are co-related. We will explore more about citric.acide in coming plots.

Distribution of SO2 and Sulphates

```{r echo=FALSE, message=FALSE, warning=FALSE}
sw1 <- p2+ geom_histogram(aes(x= free.sulfur.dioxide), fill = "blue",color= "black",binwidth = 5, alpha=0.3)+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))


sw2 <- p2+ geom_histogram(aes(x= total.sulfur.dioxide), fill = "blue",color= "black",binwidth = 10, alpha=0.3)+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))

sw3 <- p2+ geom_histogram(aes(x= sulphates), fill = "blue",color= "black",binwidth = 0.02, alpha=0.3)+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))

grid.arrange(sw1,sw2,sw3,nrow=2)
```

with few outliers, total SO2, free SO2 and sulphate seem to be normally distributed.

```{r echo=FALSE, message=FALSE, warning=FALSE}

p2+ geom_histogram(aes(x= residual.sugar), fill = "blue",color= "black",binwidth = 0.5, alpha=0.3)+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))

```

The residual sugar for white wine is definally positively skewed. 

```{r echo=FALSE, message=FALSE, warning=FALSE}

p2+ geom_histogram(aes(x= density), fill = "blue",color= "black",binwidth = 0.001, alpha=0.3)+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))


```

The density is normally distributed.

```{r echo=FALSE, message=FALSE, warning=FALSE}


p2+ geom_histogram(aes(x= alcohol), fill = "blue",color= "black",binwidth = 0.5, alpha=0.3)+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))


```

Distribution of Alcohol is positively skewed. we will explore more about alcohol and density in coming plots.

```{r echo=FALSE, message=FALSE, warning=FALSE}

p2+ geom_histogram(aes(x= chlorides), fill = "blue",color= "black",binwidth = 0.01, alpha=0.3)+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15))
```

The clorides are normally distributed with few outliers.

## Univariate Observations - for both wines
1) The acidities - fixed, volatile and citric , are normally distributed so is the pH. The acidity of wine will affect the pH as both are corelated.

2) With exception of some outliers, chlorides and density  are also normally distributed.

3) sulphates is a wine additive which can contribute to sulfur dioxide gas (S02) levels, hence we can drop one on the variables.

sulphates and total SO2 data are normally distributed, while free SO2 is positively skewed.

4) With exception of few outliers, alcohol content shows positive skewness.

5) Both the wins contain few outliers in residual sugar with value less than 1 gm/liter, which is very rare. So those data points must be errors. While compairing residual sugar content of both the wines, white wine is sweeter than red wine.

## Bivariate Plots

Let's see which variables are highly co-related, so that we can drop one of them.

First consider total SO2 and free SO2

```{r echo=FALSE, message=FALSE, warning=FALSE}

p+geom_point(aes(x=total.sulfur.dioxide,y=free.sulfur.dioxide),alpha=0.7,size = 2)+
  geom_smooth(aes(x=total.sulfur.dioxide,y=free.sulfur.dioxide))+
  ggtitle("Red Wine")+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15),
        plot.title = element_text(color= "DarkRed",size = 20))


p2+geom_point(aes(x=total.sulfur.dioxide,y=free.sulfur.dioxide),alpha=0.7,size = 2)+
  geom_smooth(aes(x=total.sulfur.dioxide,y=free.sulfur.dioxide))+
  ggtitle("White Wine")+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15),
        plot.title = element_text(color= "DarkBlue",size = 20))
```

Here we can see,except for few outliers both the variables, total SO2 and free SO2 are linearly co-related

Now,the acidities and pH co-relation

```{r echo=FALSE, message=FALSE, warning=FALSE}

p+geom_point(aes(x=pH,y=fixed.acidity),alpha=0.7,size = 2)+
  geom_smooth(aes(x=pH,y=fixed.acidity))+
  ggtitle("Red Wine")+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15),
        plot.title = element_text(color= "DarkRed",size = 20))


p+geom_point(aes(x=pH,y=volatile.acidity),alpha=0.7,size = 2)+
  geom_smooth(aes(x=pH,y=volatile.acidity))+
  ggtitle("Red Wine")+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15),
        plot.title = element_text(color= "DarkRed",size = 20))

```

PH is the measure of the degree of relative acidity versus the relative alkalinity of any liquid, on a scale of 0 to 14, with 7 being neutral. Winemakers use pH as a way to measure ripeness in relation to acidity. Low pH wines will taste tart and crisp, while higher pH wines are more susceptible to bacterial growth.

The plots show that as the pH increases, acidity decreases.

```{r echo=FALSE, message=FALSE, warning=FALSE}

p2+geom_point(aes(x=pH,y=fixed.acidity),alpha=0.7,size = 2)+
  geom_smooth(aes(x=pH,y=fixed.acidity))+
  ggtitle("White Wine")+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15),
        plot.title = element_text(color= "DarkBlue",size = 20))


p2+geom_point(aes(x=pH,y=volatile.acidity),alpha=0.7,size = 2)+
  geom_smooth(aes(x=pH,y=volatile.acidity))+
  ggtitle("White Wine")+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15),
        plot.title = element_text(color= "DarkBlue",size = 20))



p2+geom_point(aes(x=pH,y=citric.acid),alpha=0.7,size = 2)+
  geom_smooth(aes(x=pH,y=citric.acid))+
  ggtitle("White Wine")+
  theme(axis.title.x = element_text(size = 15),axis.title.y = element_text(size = 15),
        plot.title = element_text(color= "DarkBlue",size = 20))


```

The plots show that as the pH increases, acidity decreases.

#### The quality and other variable co-relation
Now let see how the various factors deciding the quality of the wine

#### for red wine
```{r echo=FALSE, message=FALSE, warning=FALSE}

p+geom_jitter(aes(x=quality,y=alcohol,group=cut_width(quality,1)),alpha=0.2)+
 geom_boxplot(aes(x=quality,y=alcohol,group=cut_width(quality,1),color=rating),size=1)+
 theme(axis.title.x = element_text(size = 15),
       axis.title.y = element_text(size = 15),
       legend.position = c(1,1),
       legend.justification = c(1,1))


```

Quality increases with higher alcohol concentration /volumn

```{r echo=FALSE, message=FALSE, warning=FALSE}



p+geom_jitter(aes(x=quality,y=density,group=cut_width(quality,1)),alpha=0.2)+
 geom_boxplot(aes(x=quality,y=density,group=cut_width(quality,1),color=rating),size=1)+
 theme(axis.title.x = element_text(size = 15),
       axis.title.y = element_text(size = 15),
       legend.position = c(1,1),
       legend.justification = c(1,1))

```

Lighter density wines have better quality

```{r echo=FALSE, message=FALSE, warning=FALSE}



p+geom_jitter(aes(x=quality,y=pH,group=cut_width(quality,1)),alpha=0.2)+
 geom_boxplot(aes(x=quality,y=pH,group=cut_width(quality,1),color=rating),size=1)+
 theme(axis.title.x = element_text(size = 15),
       axis.title.y = element_text(size = 15),
       legend.position = c(1,1),
       legend.justification = c(1,1))



```

Acidic wines are better quality wines.

```{r echo=FALSE, message=FALSE, warning=FALSE}



p+geom_jitter(aes(x=quality,y=sulphates,group=cut_width(quality,1)),alpha=0.2)+
 geom_boxplot(aes(x=quality,y=sulphates,group=cut_width(quality,1),color=rating),size=1)+
 theme(axis.title.x = element_text(size = 15),
       axis.title.y = element_text(size = 15),
       legend.position = c(1,1),
       legend.justification = c(1,1))




```

with decrease in sulphates, quality of wine decreases.

#### for white wine

```{r echo=FALSE, message=FALSE, warning=FALSE}


p2+geom_jitter(aes(x=quality,y=alcohol,group=cut_width(quality,1)),alpha=0.2)+
 geom_boxplot(aes(x=quality,y=alcohol,group=cut_width(quality,1),color=rating),size=1)+
 theme(axis.title.x = element_text(size = 15),
       axis.title.y = element_text(size = 15),
       legend.position = c(1,1),
       legend.justification = c(1,1))


```

Quality increases with higher alcohol concentration /volumn

```{r echo=FALSE, message=FALSE, warning=FALSE}


p2+geom_jitter(aes(x=quality,y=density,group=cut_width(quality,1)),alpha=0.2)+
 geom_boxplot(aes(x=quality,y=density,group=cut_width(quality,1),color=rating),size=1)+
 theme(axis.title.x = element_text(size = 15),
       axis.title.y = element_text(size = 15),
       legend.position = c(1,1),
       legend.justification = c(1,1))



```

Lighter density wines have better quality

```{r echo=FALSE, message=FALSE, warning=FALSE}

p2+geom_jitter(aes(x=quality,y=pH,group=cut_width(quality,1)),alpha=0.2)+
 geom_boxplot(aes(x=quality,y=pH,group=cut_width(quality,1),color=rating),size=1)+
 theme(axis.title.x = element_text(size = 15),
       axis.title.y = element_text(size = 15),
       legend.position = c(1,1),
       legend.justification = c(1,1))



```

Acidic wines are better quality wines.

```{r echo=FALSE, message=FALSE, warning=FALSE}


p2+geom_jitter(aes(x=quality,y=sulphates,group=cut_width(quality,1)),alpha=0.2)+
 geom_boxplot(aes(x=quality,y=sulphates,group=cut_width(quality,1),color=rating),size=1)+
 theme(axis.title.x = element_text(size = 15),
       axis.title.y = element_text(size = 15),
       legend.position = c(1,1),
       legend.justification = c(1,1))


```

with decrease in sulphates, quality of wine decreases.

## Bivariate Observations

1) Low density wines can be classified as good wines.

2) Looking at the pH plot, it is clear that as the pH of wine increases, quality of wine decreases.

3) Good quality wine has sulphates concentration to the higher side.

4) Around 12-13% of volumn alcohol content wines can be classified as good wines.
 
## Multivariate Plots
I want to compaire both type of wines. So, I am going to create a dataframe by marging both the dataframes, let's call it "wine"

```{r echo=FALSE, message=FALSE, warning=FALSE}

red_wine$wine_type <- "red"

white_wine$wine_type <- "white"

wine <- rbind(red_wine,white_wine)

wine$wine_type <- as.factor(wine$wine_type)
```

```{r}
str(wine)

summary(wine)
```

Let's compair the residual sugar content for red and white wine

```{r echo=FALSE, message=FALSE, warning=FALSE}
q <- ggplot(data = wine)

q+ geom_histogram(aes(x=residual.sugar,fill=rating),color="black",binwidth = 1)+
  xlim(0,30)+
  facet_grid(rating~wine_type, scales = "free")+
  theme(axis.title.x = element_text(size = 15),
       axis.title.y = element_text(size = 15),
       legend.position = c(1,1),
       legend.justification = c(1,1))

```

Seems like white wine is sweeter than red wine.


Lets explore the relation between density and alcohol

```{r echo=FALSE, message=FALSE, warning=FALSE}
wine$rating <- as.character(wine$rating)

ggplot(data = wine,
       aes(x=alcohol,
           y= density,
           color= rating), size = 4) +
  coord_cartesian(ylim =  c(0.985,1.002),
                  xlim =  c(7.5,15)) +
  geom_jitter(size = 1) +
  geom_smooth(method = "lm", fill= NA) +
  scale_y_continuous(breaks = seq(0.985,1.002,0.002)) +
  scale_color_brewer(type = "seq",guide = guide_legend(title = "Wine Quality")) +
  
  facet_grid(.~wine_type, scales = "free")+
   theme(axis.title.x = element_text(size = 15),
       axis.title.y = element_text(size = 15),
       legend.position = c(1,1),
       legend.justification = c(1,1))
  
 
```

From the plot, it is clear that with constant alcohol contaent, density does not play much role in defining the quality of wine.

The co-relation between alocohol and fixed acidity

```{r echo=FALSE, message=FALSE, warning=FALSE}

ggplot(data = wine,
       aes(x=alcohol,
           y= citric.acid,
           color= rating), size = 4) +
  coord_cartesian(ylim =  c(0,1.05)) +
  geom_jitter(size = 1) +
  geom_smooth(method = "lm", fill= NA) +
  
  scale_color_brewer(type = "seq",guide = guide_legend(title = "Wine Quality")) +
  
  facet_grid(.~wine_type, scales = "free")+
   theme(axis.title.x = element_text(size = 15),
       axis.title.y = element_text(size = 15),
       legend.position = c(1,1),
       legend.justification = c(1,1))

```

The plot shows that there is no co-relation. But we can see there are some wines with zero citric acide concentration. I would like to understand, are there any wines with no citric acide or this is due to error in data collection.

### The co-realation between variables

Corealtion Matrix

```{r echo=FALSE, message=FALSE, warning=FALSE}

cor1 <- ggcorr(red_wine,
               nbreaks = 4, palette = "PuOr",
       label = TRUE,label_alpha = 0.7,
       name = "Wine Correaltion Coff.",
       hjust=0.8, angle = -70, size = 3)+
  ggplot2::labs(title = "for Red Wine")

cor2 <- ggcorr(white_wine,
               nbreaks = 4, palette = "PuOr",
       label = TRUE,label_alpha = 0.7,
       name = "Wine Correaltion Coff.",
       hjust=0.8, angle = -70, size = 3)+
  ggplot2::labs(title = "for White Wine")

cor1

```

Not very strong correlation between the variables and quantity of wine, alcohol content and volatile acidity can be taken into consideration. 

```{r echo=FALSE, message=FALSE, warning=FALSE}

cor2

```
For white wine, only alcohol seems to be quality deciding factor. 

## Multivariate Observations
Though some variables show strong co-relation, only alchole and sulphates show some co-relation with quality of wine.

## Final Plots and Summary
I chose these three plots to showcase the final summary of this data exploration

1)Quality and rating

```{r echo=FALSE, message=FALSE, warning=FALSE}

grid.arrange(qua_r,rating_r,qua_w, rating_w, nrow= 2)
 

```

We have most of the avarage class wines in the data set, that could make the algorithm to predict only the avarage class with precision.


2) the residual sugar content for red and white wine - 

```{r echo=FALSE, message=FALSE, warning=FALSE}

q+ geom_histogram(aes(x=residual.sugar,fill=rating),color="black",binwidth = 1)+
  xlim(0,30)+
  facet_grid(rating~wine_type, scales = "free")+
  theme(axis.title.x = element_text(size = 15),
       axis.title.y = element_text(size = 15),
       legend.position = c(1,1),
       legend.justification = c(1,1)) +

  xlab("Residual Sugar(mg/l)") + 
  ylab("Wine Count ") +
  ggtitle("Sweetness Of Wine")
   
  

```

The above plot shows that white wine have sweeter varieties of wines than red wine.

3)exploring alcohol (% by volumn) and density (mg/l) 

```{r echo=FALSE, message=FALSE, warning=FALSE}

ggplot(data = wine,
       aes(x=alcohol,
           y= density,
           color= rating), size = 4) +
  coord_cartesian(ylim =  c(0.985,1.002),
                  xlim =  c(7.5,15)) +
  geom_jitter(size = 1) +
  geom_smooth(method = "lm", fill= NA) +
  scale_y_continuous(breaks = seq(0.985,1.002,0.002)) +
  scale_color_brewer(type = "seq",guide = guide_legend(title = "Wine Quality")) +
 
  facet_grid(.~wine_type, scales = "free") +
  
   theme(axis.title.x = element_text(size = 15),
       axis.title.y = element_text(size = 15),
       legend.position = c(1,1),
       legend.justification = c(1,1)) +
  xlab("Alcohol (% by Volumn)") +
  ylab("Density (mg/l)") +
  ggtitle("Alcohol Density Correlation")
  
```

Though density does not affect wine quality, we can say lighter density and high alcohol % by volumn wine could be classified as good quality wine

## Refection 

Initial exploration of data showed that data is not balanced, "avarage" class wine contains most of the data compaired to "bad" and "good" class.

Further in the process, I tried to see the distribution of different variables through Univariate Plots. Mostly all are normally distributed. Main issue I came across was that there are a lot of outliers present in some variables. This could possiably be the bad data collected through error.

Give that there is not a strong co-relation between variables and quality of wine, it is kind of defficult to determine which variable could be tweaked to improve the quality of wine.

To overcome this issue, I would prefer to collect more data and then with feature engineering we could get the better algorithm to classify the wines.

Having said, this was a fun project to work on and learn along the way. 






